---
title: "Math1005 Project 1 (Group)"
author: "Students SID 530646424, number_1, number_2, number_3"
subtitle: "Project Covid Impact on Transport"
date: "University of Sydney | Math1005 | Lab Class XXXXX"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

<br>

# Executive Summary
- The aim of this report is to show how covid-19 has impacted NSW transport before and during the outbreak.
- The main discoveries are (add text)

<br>

# Full Report
## Initial Data Analysis (IDA)

- The data came from: NSW Government Traffic Volume Viewer
- The data is/is not valid because (add text)
- Possible issues include (add text)
- Potential stakeholders include (add text)
- Each row represents (add text)
- Each column represents (add text)
- The key variables are (add text)

```{r}
## read in data

## show classification of variables

```
- Total small vehicles in specific years. 
- Total large vehicles in specific years. 
- Total vehicles in specific years. 
- % change in heavy vehicles before and after covid 
- % change in light vehicles before and after covid 

<br>

## Research Question 1: Compare how traffic data has been impacted by COVID. Look at Pre-covid year and in-covid year (2019vs2021). Looking at Burns Bay Rd 

Linear regression using daily traffic data 
```{r}
## write code here

```
- insert graph above this line^^^

<br>

## Research Question 2: How has this impacted on Heavy vs Light vehicles (looking at a residential road vs a commercial route). 

Insert text and analysis. 

```{r}
## write code here

```
- insert graph above this line^^^

<br>

## Extra Question: Compare data to another road

Insert text and analysis. 

```{r}
## write code here

```
- insert graph above this line^^^

<br>

# References

Put references here in APA format.
